---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# baseballvizR

<!-- badges: start -->
<!-- badges: end -->

The goal of `baseballvizR` is to provide functions to easily digest baseball statistics taken from raw statcast data.

## Installation

You can install the development version of project from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
# install.packages("devtools")
devtools::install_github("ADC-405-S26/baseballvizR")
```

## No Dataset

There is no dataset added to this package. Each function in this package utilizes 'baseballr' functions to webscrape data every time a function in this package is run. Because each function scrapes the data on its own, ther eis no need for a dataset to run tests with.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(baseballvizR)
```

#### plot_zone_heatmap example

```{r}
plot_zone_heatmap("Juan","Soto", "2024-05-19", "2025-06-05", playerIndex = 6)
```

#### plot_spray_chart example

```{r}
plot_spray_chart("Juan","Soto", "2024-05-19", "2025-06-05", playerIndex = 6)
```

#### calculate_hitter_profile example

```{r}
calculate_hitter_profile("Juan","Soto", "2024-05-19", "2025-06-05", playerIndex = 6)
```
