---
title: "Introduction to baseballvizR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to baseballvizR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `baseballvizR` package provides convenience functions for some common tasks. I wanted to make this package because baseball statistics are just numbers on a page and don't always tell the full story. With the functions in this package you can get a glimpse behind just the raw data and start to see trends. 

To install this package from GitHub, use

```{r, eval=FALSE}
install.packages("remotes")
install.packages("devtools")
devtools::install_github("BillPetti/baseballr")
devtools::install_github("ADC-405-S26/baseballvizR", force = TRUE)
```

Load the package using the following code.

```{r setup}
library(baseballvizR)
```

The package contains three functions

* `plot_zone_heatmap`

* `plot_spray_chart`
* `calculate_hitter_profile`

## Example

Here is an example of how to use each of these functions. 

Each function makes use of a players first and last name, the start date and end date of the period you want to extract data from, and the player index. The player index is for when there is more than one player with the same name, and you need to choose between them. Every time you run the function, it will produce a table with every player that has the name name inputted in the function. You can adjust the player index to select one of these players.

The first function `plot_zone_heatmap` takes a players data from a specified time period, and displays a heat map of batting average based on the pitches location.

```{r}
plot_zone_heatmap("Juan","Soto", "2024-05-19", "2025-06-05", playerIndex = 6)
```

The second function `plot_spray_chart` takes a players data from a specified time period, and displays a spray chart of where the ball was hit. It then color codes each data point based on the outcome of the play.

```{r}
plot_spray_chart("Juan","Soto", "2024-05-19", "2025-06-05", playerIndex = 6)
```

The third function `calculate_hitter_profile` takes a players data from a specified time period, and displays a table of all of the accumulated stats over that period.

```{r}
calculate_hitter_profile("Juan","Soto", "2024-05-19", "2025-06-05", playerIndex = 6)
```
